### 2020-05-26 README.Rmd
update README

<!-- badges: start -->
[![R CMD Check via {tic}](https://github.com/mlr-org/mlr3spatiotempcv/workflows/R%20CMD%20Check%20via%20{tic}/badge.svg?branch=master)](https://github.com/mlr-org/mlr3spatiotempcv/actions)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->

This package extends the [mlr3](https://github.com/mlr-org/mlr3) package framework by spatiotemporal resampling and visualization methods.

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |

@@

### Visualization of all partitions

@@

### Visualization of the first fold only

>>>>

<!-- badges: start -->
[![R CMD Check via {tic}](https://github.com/mlr-org/mlr3spatiotempcv/workflows/R%20CMD%20Check%20via%20{tic}/badge.svg?branch=master)](https://github.com/mlr-org/mlr3spatiotempcv/actions)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This package extends the [mlr3](https://github.com/mlr-org/mlr3) package framework with spatiotemporal resampling and visualization methods.

⚠️⚠️⚠️  
The package is in very early stages and breaking changes withour further notice are expected.
If you want to use if for your research, you might need to refactor your analysis along the way.  
⚠️⚠️⚠️

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |
| cookfarm | `tsk("cookfarm")` | Regr    |

@@

### Visualization of all folds

@@

### Visualization of a specific fold
